Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Citation

\subsubsection{Speech Processing Component}
The {\em Speech Processing Component} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}. Requests are made through an API Singleton that is constructed on game load. These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data. Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers. When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads. Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
\begin{enumerate}
  \item
    Web Workers are initalized to start processing the audio stream in parallel.
  \item
    Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
  \item
    Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
\end{enumerate}
Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}. The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx Component} to iterate a best guess for the correctness of the child's speech.

\subsubsection{CMU Sphinx Component}

>>>>

\subsubsection{Speech Processing}
The {\em Speech Processing} of the Kimbee system handles all audio processing and speech related requests from the {\em Phaser Game Implementation}. Requests are made through an API Singleton that is constructed on game load. These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data. Harvesting and processing microphone levels is a multithreaded process implemented with HTML5 Web Workers. When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in seperate threads. Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
\begin{enumerate}
  \item
    Web Workers are initalized to start processing the audio stream in parallel.
  \item
    Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
  \item
    Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
\end{enumerate}
Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}. The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx} to iterate a best guess for the correctness of the child's speech.

\subsubsection{CMU Sphinx}

CITATION FOR AARON \cite{CMU:Sphinx}.
